%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://sourabhbajaj.com/}{\Large Brandon Chong}} & Email : \href{mailto:iam@brandonchong.com}{iam@brandonchong.com}\\
  \href{http://brandonchong.com/}{http://www.brandonchong.com} \\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Neeva}{Mountain View, CA}
      {Software Engineer}{Jul. 2020 - Present}
      \resumeItemListStart
        \resumeItem{Reddit Summarization}
          {Led product decisions and client-side development.}
        \resumeItem{Forums discussion onebox (Reddit, StackOverflow, and Quora)}
          {Client-side integration of distinguised forum discussions UI+UX onto the Neeva search page.}
        \resumeItem{Full-page search experiences (FPE)}
          {Immersive user interfaces and experiences for sports and travel queries.}
        \resumeItem{NewsGuard}
          {Client-side implementation for letting users view NewsGuard ratings regarding a domain (i.e. how trustable it is, etc)}
        \resumeItem{Preferred providers}
          {Client-side implementation for letting users determine what domains they would like to see more of and less of in the search results.}
        \resumeItem{Currency conversion, translation, sports, and lyrics oneboxes}
          {Tablestakes features to reach parity with other search engines for presenting simple quick answers on specific queries.}
        \resumeItem{LensBang}
          {Client-side implementation allowing DuckDuckGo-like search re-direction and Neeva search result filtering.}
        \resumeItem{GeoLocation prompt}
          {Client-side implementation to prompt a user to submit their device location for an enhanced searching experience.}
        \resumeItem{Neeva Maps (Apple Maps ver.)}
          {Client-side implementation for integrating Apple Maps into Neeva Maps.}
        \resumeItem{Neeva Maps + Directions (Google Maps ver.)}
          {Client-side implementation for integrating Google Maps into Neeva Maps and Directions.}
      \resumeItemListEnd
      
    \resumeSubheading
      {University of Washington: College of Engineering}{Seattle, WA}
      {Student Web Developer}{Feb. 2018 - Jun. 2020}
      \resumeItemListStart
        \resumeItem{UAPP engineering major application}
          {Application for students to apply for their desired engineering major and for admins to review applications. Worked across the stack to revamp UI, address bugs/issues, and maintain existing logic.}
        \resumeItem{Engineering scholarship application}
          {Application for students to submit their scholarship application for review and for admins to review applications. Worked across the stack to revamp UI, address bugs/issues, and maintain existing logic.}
        \resumeItem{Engineering faculty software request application}
          {Application for faculty to submit their request for needed software (e.g. AutoCAD, MatLab, etc) and for admins to review requests. Worked across the stack to revamp UI, address bugs/issues, and maintain existing logic.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Washington}{Seattle, WA}
      {Bachelor of Science in Informatics}{Sep. 2016 - Jun. 2020}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Personal Site}
      {Personal site written with GatsbyJS, TypeScript, Vercel serverless functions, and AWS DynamoDB.}
    \resumeSubItem{Chemodel 3D and AR}
      {iOS app to render chemical molecule structures in 3D using augmented reality.}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Javascript, TypeScript, Go, CSS}
      \hfill
      \textbf{Technologies}{: React, NodeJS}
    }
  \resumeSubHeadingListEnd


\end{document}
